### 2016-04-06 text/ms.Rmd
Wrap the manuscript for editing by voice
Editing of the main manuscript file

One solution is to take the average or weighted average of several model
predictions, i.e. an ensemble. Such ensembles are typically more accurate and
less biased than individual model estimates and can integrate uncertainty in
model structure, initial conditions, and parameter estimation [@dietterich2000;
@araujo2007]. Ensembles are superior to individual models for at least three
reasons including statistical, computational, and representational reasons
[@dietterich2000]. Statistically by averaging across models representing
different hypotheses about reality, computationally by reducing the risk of
getting stuck in a local optima, and representationally he by expanding
representational form<!--explain how this is possible.--> This approach forms
the basis of many machine learning methods [e.g. @dietterich2000], has helped
reconcile climate forecasts from dozens of models [e.g. @murphy2004;
@tebaldi2007; @ipcc2013], and even improved early warning signs of malaria
outbreaks [@thomson2006]. In ecology, ensemble methods are sometimes used to
improve species distribution modelling [e.g. @araujo2007; @breiner2015] and
indeed have been used to combine estimates of population status and trend [e.g.
@brodziak2010].

Whereas averages or weighted averages of model estimates may improve
predictions compared to a single model, they may not optimally leverage
available data. The best prediction does not necessarily lie in the middle of
multiple model predictions, some models may perform better than others in
certain conditions, and the covariance between models may contain information
that can improve predictive accuracy. <!--can you give an example here? e.g.
a model may behave poorly at estimating low biomass. By training the
superensbmeles models with real data, it can identify the pros and cons of each
model and incorporate them into the estimates. .--> We can exploit these
characteristics by using the predictions from a group of models as inputs into
a separate statistical model. This technique, sometimes called superensemble
modelling [@krishnamurti1999], is common in climate and weather forecasting
[e.g. @yun2005; @mote2015]. The superensemble is fit to a training dataset
where outcomes are well known and then used to predict on a dataset of interest
(Fig. \ref{didactic}). For example, @krishnamurti1999 combined predictions of
wind and precipitation in Asian monsoons via a superensemble regression fit to
observed data. Their superensemble was considerably more accurate than any
individual prediction or weighted average of predictions.

In fisheries science, the commonly used operational models for determining
status and trend of exploited fish populations are stock assessments, i.e.,
population models coupled to an observation model, that incorporate all
appropriate data (e.g. catches, size and age distributions, surveys, and
tagging information) to quantify values such as the biomass of a stock that can
produce maximum sustainable yield ($B_\mathrm{MSY}$) [@hilborn1992]. However,
the broad range of data required to conduct these stock assessments are not
available for the majority of fish populations, including those of conservation
concern and of economic interest to fisheries [@fao2014]. Therefore, a number
of models have been proposed to assess $B/B_\mathrm{MSY}$ based on the limited
data available for the majority of fish stocks: (1) a time series of the total
biomass of catch and (2) a basic understanding of population productivity [e.g.
@vasconcellos2005; @martell2013]. Recently, @rosenberg2014 investigated the
performance of four data-limited models through a large-scale simulation
experiment. Three of these models are based on Schaefer (logistic) biomass
dynamics and one is an empirical model fitted to more data-rich stock
assessment output. The four models frequently disagreed about population
status, no one model had strong performance across all fish stocks, and some
models performed better than others depending on circumstances (e.g. Fig.
\ref{motivate}).

@@

<!-- TODO: It might be good to throw in a single sentence here describing the
4 models, or at least listing them and maybe a couple key differences among
them.-->

@@

@@

We fit four individual data-limited models that use data on catch and basic life
history parameters to estimate $B/B_\mathrm{MSY}$. <!-- explain why we choose
these models not others? --> Three of the models are mechanistic and based
generally on Schaefer biomass dynamics [@schaefer1954] of the form

@@

>>>>

One solution is to take the average or weighted average of several model
predictions, i.e. an ensemble. Such ensembles are typically more accurate and
less biased than individual model estimates and can integrate uncertainty in
model structure, initial conditions, and parameter estimation
[@dietterich2000; @araujo2007]. Ensembles are superior to individual models
for at least three reasons: statistically by averaging across models and
therefore being less likely to pick the "wrong" model, computationally by
reducing the risk of getting stuck in a local optima, and representationally
by expanding the range of hypotheses explored [@dietterich2000]. This approach
forms the basis of many machine learning methods [e.g. @dietterich2000], has
helped reconcile climate forecasts from dozens of models [e.g. @murphy2004;
@tebaldi2007; @ipcc2013], and even improved early warning signs of malaria
outbreaks [@thomson2006]. In ecology, ensemble methods are sometimes used to
improve species distribution modelling [e.g. @araujo2007; @breiner2015] and
indeed have been used to combine estimates of population status and trend
[e.g. @brodziak2010].

Whereas averages or weighted averages of model estimates may improve
predictions compared to a single model, they may not optimally leverage
available data. The best prediction does not necessarily lie in the middle of
multiple model predictions, some models may perform better than others in
certain conditions, and the covariance between models may contain information
that can improve predictive accuracy. For example, one model might perform
well at estimating high levels of abundance but be biased at low levels of
abundance, while another model might have the opposite properties. An optimal
combination of these models is not simply an average of the two.

We can exploit these characteristics by using the predictions from a group of
models as inputs into a separate statistical model. This technique, sometimes
called superensemble modelling [@krishnamurti1999], is common in climate and
weather forecasting [e.g. @yun2005; @mote2015]. The superensemble is fit to a
training dataset where outcomes are well known and then used to predict on a
dataset of interest (Fig. \ref{didactic}). For example, @krishnamurti1999
combined predictions of wind and precipitation in Asian monsoons via a
superensemble regression fit to observed data. Their superensemble was
considerably more accurate than any individual prediction or weighted average
of predictions.

In fisheries science, the commonly used operational models for determining
status and trend of exploited fish populations are stock assessments, i.e.,
population models coupled to an observation model, that incorporate all
appropriate data (e.g. catches, size and age distributions, surveys, and
tagging information) to quantify values such as the biomass of a stock that
can produce maximum sustainable yield ($B_\mathrm{MSY}$) [@hilborn1992].
However, the broad range of data required to conduct these stock assessments
are not available for the majority of fish populations, including those of
conservation concern and of economic interest to fisheries [@fao2014].

Therefore, a number of models have been proposed to assess $B/B_\mathrm{MSY}$
based on the limited data available for the majority of fish stocks: (1)
a time series of the total biomass of catch and (2) a basic understanding of
population productivity [e.g. @vasconcellos2005; @martell2013]. Recently,
@rosenberg2014 investigated the performance of four data-limited models
through a large-scale simulation experiment. Three of these models are based
on Schaefer (logistic) biomass dynamics and one is an empirical model fitted
to more data-rich stock assessment output. The four models frequently
disagreed about population status, no one model had strong performance across
all fish stocks, and some models performed better than others depending on
circumstances (e.g. Fig. \ref{motivate}).

@@

@@

<!-- TODO Add a summary of the methods here  -->

@@

We fit four individual data-limited models that use data on catch and basic
life history parameters to estimate $B/B_\mathrm{MSY}$. We chose these models
because TODO. Three of the models are mechanistic and based generally on
Schaefer biomass dynamics [@schaefer1954] of the form

@@

## Simulated data set to build the ensemble TODO: finish this
